%Fred, Simon, Sou-Cheng, Yuhan, NSF Grant Dec 2022
% GitHub:https://github.com/fjhickernell/NSF_2020_CDSE_MSS
% Overleaf: https://www.overleaf.com/project/5f3edbef9ad56800017ed20a
\documentclass[11pt]{NSFamsart}
%\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{latexsym,amsfonts,amsmath,amssymb,amsthm,epsfig,extdash,multirow}
\usepackage{stackrel,tabularx,mathtools,longtable,xspace}
\usepackage[shortlabels]{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{accents, booktabs}
\usepackage{algorithm, algorithmicx}
\usepackage{anyfontsize}
\usepackage[capitalise]{cleveref}
\usepackage{wrapfig}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[normalem]{ulem}
\usepackage{bbm}
\usepackage[compact]{titlesec}
\titlelabel{\thetitle.\,}
%\titleformat*{\section}{\scshape}
%\titleformat{\section}{block}{thesection}{1ex}{}
%\titlespacing{\section}{0pt}{*0}{*0}
% \titlespacing{\subsection}{0pt}{*0}{*0}
% \titlespacing{\subsubsection}{0pt}{*0}{*0}
\crefformat{equation}{(#2#1#3)}


\voffset 0.23in
\hoffset 0in
\textheight 8.9in
\textwidth6.45in
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\headsep-0.6in
\thispagestyle{empty} \pagestyle{empty} %to eliminate page numbers for upload
%\thispagestyle{plain} \pagestyle{plain} %to add back page numbers
\renewcommand{\baselinestretch}{0.98} %to squeeze the lines a bit

\crefname{section}{Sect.}{Sects.}
\crefname{figure}{Fig.}{Figs.}


\usepackage{minted}
\newminted{python}{frame=lines,framerule=1.5pt,breaklines=true}
\newmintinline[pyinline]{python}{}


\usepackage{algpseudocode}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

%\usepackage{showlabels}
\newcommand{\Upara}[1]{\noindent\underline{#1}:\xspace}
\newcommand{\cmtS}[1]{{\color{blue}{(Simon: #1)}}}

\newcommand{\myshade}{60}
\colorlet{mylinkcolor}{violet}
\colorlet{mycitecolor}{violet}
%\colorlet{mycitecolor}{OliveGreen}
\colorlet{myurlcolor}{YellowOrange}

\hypersetup{
	linkcolor  = mylinkcolor!\myshade!black,
	citecolor  = mycitecolor!\myshade!black,
	urlcolor   = myurlcolor!\myshade!black,
	colorlinks = true,
}


% This package prints the labels in the margin
%\usepackage[notref,notcite]{showkeys}


%%list of acronyms with links
\newcommand{\FH}{\hyperlink{FHlink}{FH}\xspace}
\newcommand{\SM}{\hyperlink{SMlink}{SM}\xspace}
\newcommand{\SCTC}{\hyperlink{SCTClink}{SCTC}\xspace}
\newcommand{\AO}{\hyperlink{AOlink}{AO}\xspace}
\newcommand{\MM}{\hyperlink{MMlink}{MM}\xspace}
\newcommand{\CH}{\hyperlink{CHlink}{CH}\xspace}
\newcommand{\CO}{\hyperlink{COlink}{CO}\xspace}
\newcommand{\TS}{\hyperlink{TSlink}{TS}\xspace}
\newcommand{\IJi}{\hyperlink{IJlink}{IJ}\xspace}
\newcommand{\JM}{\hyperlink{JMlink}{JM}\xspace}
\newcommand{\KL}{\hyperlink{KLlink}{KL}\xspace}
\newcommand{\FS}{\hyperlink{FSlink}{FS}\xspace}
\newcommand{\TT}{\hyperlink{TTlink}{TT}\xspace}
\newcommand{\RZ}{\hyperlink{RZlink}{RZ}\xspace}
\newcommand{\GEF}{\hyperlink{GEFlink}{GEF}\xspace}
\newcommand{\YD}{\hyperlink{YDlink}{YD}\xspace}
\newcommand{\JR}{\hyperlink{JRlink}{JR}\xspace}
\newcommand{\LlAJR}{\hyperlink{LlAJRlink}{LlAJR}\xspace}
\newcommand{\IID}{\hyperlink{IIDlink}{IID}\xspace}
\newcommand{\LD}{\hyperlink{LDlink}{LD}\xspace}
\newcommand{\LJ}{\hyperlink{LJlink}{LJ}\xspace}
\newcommand{\XT}{\hyperlink{XTlink}{XT}\xspace}
\newcommand{\KZ}{\hyperlink{KZlink}{KZ}\xspace}
\newcommand{\DL}{\hyperlink{DLlink}{DL}\xspace}
\newcommand{\XZ}{\hyperlink{XZlink}{KZ}\xspace}
\newcommand{\JL}{\hyperlink{JLlink}{JL}\xspace}
\newcommand{\YZ}{\hyperlink{YZlink}{YZ}\xspace}
\newcommand{\AS}{\hyperlink{ASlink}{AS}\xspace}
\newcommand{\CLT}{\hyperlink{CLTlink}{CLT}\xspace}
\newcommand{\PN}{\hyperlink{PNlink}{PN}\xspace}
\newcommand{\PR}{\hyperlink{PRlink}{PR}\xspace}
%\newcommand{\DN}{\hyperlink{DNlink}{DN}\xspace}
\newcommand{\BO}{\hyperlink{BOlink}{BO}\xspace}
\newcommand{\QMC}{\hyperlink{QMClink}{QMC}\xspace}
\newcommand{\QMCPy}{\hyperlink{QMCPylink}{QMCPy}\xspace}
\newcommand{\UAV}{\hyperlink{UAVlink}{UAV}\xspace}
\newcommand{\LimOne}{\hyperlink{LimOneLink}{Limitation 1}\xspace}
\newcommand{\LimTwo}{\hyperlink{LimTwoLink}{Limitation 2}\xspace}
\newcommand{\LimThree}{\hyperlink{LimThreeLink}{Limitation 3}\xspace}
\newcommand{\LimFour}{\hyperlink{LimFourLink}{Limitation 4}\xspace}
\newcommand{\LimFive}{\hyperlink{LimFiveLink}{Limitation 5}\xspace}
\newcommand{\LimSix}{\hyperlink{LimSixLink}{Limitation 6}\xspace}
\newcommand{\JETSCAPE}{\hyperlink{JetscapeLink}{JETSCAPE}\xspace}


\newcommand{\SEC}{Sect.\xspace}


\newcommand{\QMCSoft}{QMCSoft\xspace}
%\newcommand{\QMCPy}{QMCPy\xspace}
\newcommand{\GAIL}{GAIL\xspace}
%\newcommand{\QMC}{QMC\xspace}
\newcommand{\IIDMC}{IID MC\xspace}
\newcommand{\SAMSIQMC}{SAMSI-QMC\xspace}
\newcommand{\SciPy}{SciPy\xspace}
\newcommand{\TensorFlow}{TensorFlow\xspace}
\newcommand{\GSL}{GSL\xspace}
\newcommand{\NAG}{NAG\xspace}
\newcommand{\MATLAB}{MATLAB\xspace}
\newcommand{\PyTorch}{PyTorch\xspace}
\newcommand{\Chebfun}{Chebfun\xspace}
\newcommand{\Rlang}{R\xspace}
\newcommand{\Julia}{Julia\xspace}


%\textheight9.1in

\newtheorem{theorem}{Theorem}


\providecommand{\FJHickernell}{Hickernell}
\newcommand{\hf}{\widehat{f}}
\newcommand{\hg}{\widehat{g}}
\newcommand{\hI}{\hat{I}}
\newcommand{\hatf}{\hat{f}}
\newcommand{\hatg}{\hat{g}}
\newcommand{\tf}{\widetilde{f}}
\newcommand{\tbf}{\tilde{\bff}}
%\DeclareMathOperator{\Pr}{\mathbb{P}}

% Math operators
\DeclareMathOperator{\std}{std}
\DeclareMathOperator{\cost}{COST}
\DeclareMathOperator{\comp}{COMP}
\DeclareMathOperator{\loss}{loss}
\DeclareMathOperator{\lof}{lof}
\DeclareMathOperator{\reg}{reg}
\DeclareMathOperator{\CV}{CV}
\DeclareMathOperator{\size}{wd}
\DeclareMathOperator{\GP}{\mathcal{G} \! \mathcal{P}}
\DeclareMathOperator{\erf}{erf}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\QOI}{QOI} %Quantity of Interest
\DeclareMathOperator{\POI}{POI} %Parameter of Interest
\DeclareMathOperator{\Ans}{ANS}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\APP}{\widehat{\QOI}}
\DeclareMathOperator{\SURR}{SM} %surrogate model
\DeclareMathOperator{\STREND}{ST} %surrogate trend
\DeclareMathOperator{\SVAR}{SV} %surrogate variation
\DeclareMathOperator{\SVARERR}{SVU} %surrogate variation uncertainty
\newcommand{\MLS}{\textrm{MLS}\xspace} %distance weighted least squares, also known as moving least squares
%\DeclareMathOperator{\ALG}{ALG}
\DeclareMathOperator{\ERR}{ERR}
\DeclareMathOperator{\VAL}{ACQ}
\DeclareMathOperator{\OPER}{OPER}
\DeclareMathOperator{\INT}{INT}
\DeclareMathOperator{\MIN}{MIN}
\DeclareMathOperator{\ID}{ID}
\DeclareMathOperator{\APPMIN}{\widehat{\MIN}}
\DeclareMathOperator{\APPID}{\widehat{\ID}}
\DeclareMathOperator{\MINVAL}{MINACQ}
\DeclareMathOperator{\IDVAL}{IDACQ}
\DeclareMathOperator{\SURRERR}{SU}
\DeclareMathOperator{\MINERR}{MERR}
\DeclareMathOperator{\IDERR}{IDERR}
\DeclareMathOperator{\Prob}{\mathbb{P}}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\filldis}{fill}
\DeclareMathOperator{\sep}{sep}
\DeclareMathOperator{\avg}{avg}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\cov}{cov}
\newcommand{\TREND}{\textup{T}}
\newcommand{\VAR}{\textup{V}}
\newcommand{\LS}{\textup{LS}}
\newcommand{\unif}{\textup{unif}}
\newcommand{\fidparam}{\bldeta}







\newcommand{\reals}{{\mathbb{R}}}
\newcommand{\naturals}{{\mathbb{N}}}
\newcommand{\natzero}{{\mathbb{N}_0}}
\newcommand{\integers}{{\mathbb{Z}}}
\def\expect{{\mathbb{E}}}
\def\il{\left \langle}
\def\ir{\right \rangle}
\def\e{\varepsilon}
\def\g{\gamma}
\def\l{\lambda}
\def\b{\beta}
\def\a{\alpha}
\def\lall{\Lambda^{{\rm all}}}
\def\lstd{\Lambda^{{\rm std}}}

\newcommand{\vf}{\boldsymbol{f}}
\newcommand{\hV}{\widehat{V}}
\newcommand{\tV}{\widetilde{V}}
\newcommand{\fraku}{\mathfrak{u}}
\newcommand{\hcut}{\mathfrak{h}}
\newcommand{\tOmega}{\widetilde{\Omega}}
\newcommand{\tvarrho}{\widetilde{\varrho}}

\newcommand{\bbE}{\mathbb{E}}
\newcommand{\tQ}{\widetilde{Q}}
\newcommand{\mA}{\mathsf{A}}
\newcommand{\mB}{\mathsf{B}}
\newcommand{\mC}{\mathsf{C}}
\newcommand{\mD}{\mathsf{D}}
\newcommand{\mG}{\mathsf{G}}
\newcommand{\mH}{\mathsf{H}}
\newcommand{\mI}{\mathsf{I}}
\newcommand{\bbK}{\mathbb{K}}
\newcommand{\mK}{\mathsf{K}}
\newcommand{\tmK}{\widetilde{\mathsf{K}}}
\newcommand{\mL}{\mathsf{L}}
\newcommand{\mM}{\mathsf{M}}
\newcommand{\mP}{\mathsf{P}}
\newcommand{\bbP}{\mathbb{P}}
\newcommand{\mQ}{\mathsf{Q}}
\newcommand{\mR}{\mathsf{R}}
\newcommand{\mX}{\mathsf{X}}
\newcommand{\mPhi}{\mathsf{\Phi}}
\newcommand{\mPsi}{\mathsf{\Psi}}
\newcommand{\mLambda}{\mathsf{\Lambda}}
\newcommand{\mSigma}{\mathsf{\Sigma}}
\newcommand{\cube}{[0,1]^d}
\newcommand{\design}{\{\bx_i\}_{i=1}^n}
\newcommand{\bbone}{\mathbbm{1}}




\newcommand{\bone}{\boldsymbol{1}}
\newcommand{\bzero}{\boldsymbol{0}}
\newcommand{\binf}{\boldsymbol{\infty}}
\newcommand{\ba}{{\boldsymbol{a}}}
\newcommand{\bb}{{\boldsymbol{b}}}
\newcommand{\bc}{{\boldsymbol{c}}}
\newcommand{\bd}{{\boldsymbol{d}}}
\newcommand{\be}{{\boldsymbol{e}}}
\newcommand{\bff}{{\boldsymbol{f}}}
\newcommand{\bhh}{{\boldsymbol{h}}}
\newcommand{\beps}{{\boldsymbol{\varepsilon}}}
\newcommand{\tbeps}{\tilde{\beps}}
\newcommand{\bt}{{\boldsymbol{t}}}
\newcommand{\bT}{{\boldsymbol{T}}}
\newcommand{\bx}{{\boldsymbol{x}}}
\newcommand{\bX}{{\boldsymbol{X}}}
\newcommand{\bh}{{\boldsymbol{h}}}
\newcommand{\bj}{{\boldsymbol{j}}}
\newcommand{\bk}{{\boldsymbol{k}}}
\newcommand{\bg}{{\boldsymbol{g}}}
\newcommand{\bn}{{\boldsymbol{n}}}
\newcommand{\br}{{\boldsymbol{r}}}
\newcommand{\bv}{{\boldsymbol{v}}}
\newcommand{\bu}{{\boldsymbol{u}}}
\newcommand{\by}{{\boldsymbol{y}}}
\newcommand{\bY}{{\boldsymbol{Y}}}
\newcommand{\bz}{{\boldsymbol{z}}}
\newcommand{\bZ}{{\boldsymbol{Z}}}
\newcommand{\bvarphi}{{\boldsymbol{\varphi}}}
\newcommand{\bgamma}{{\boldsymbol{\gamma}}}
\newcommand{\bphi}{{\boldsymbol{\phi}}}
\newcommand{\bpsi}{{\boldsymbol{\psi}}}
\newcommand{\bPsi}{{\boldsymbol{\Psi}}}
\newcommand{\btheta}{{\boldsymbol{\theta}}}
\newcommand{\bmu}{\boldsymbol{\mu}}
\newcommand{\bnu}{{\boldsymbol{\nu}}}
\newcommand{\balpha}{{\boldsymbol{\alpha}}}
\newcommand{\bbeta}{{\boldsymbol{\beta}}}
\newcommand{\bldeta}{{\boldsymbol{\eta}}}
\newcommand{\bo}{{\boldsymbol{\omega}}}  %GF added
\newcommand{\newton}[2]{\left(\begin{array}{c} #1\\ #2\end{array}\right)}
\newcommand{\anor}[2]{\| #1\|_{\mu_{#2}}}
\newcommand{\satop}[2]{\stackrel{\scriptstyle{#1}}{\scriptstyle{#2}}}
\newcommand{\setu}{{\mathfrak{u}}}

\newcommand{\me}{\textup{e}}
\newcommand{\mi}{\textup{i}}
\def\d{\textup{d}}
\def\dif{\textup{d}}
\newcommand{\cc}{\mathcal{C}}
\newcommand{\cb}{\mathcal{B}}
\newcommand{\cl}{L}
\newcommand{\ct}{\mathfrak{T}}
\newcommand{\cx}{{\Omega}}
\newcommand{\cala}{{\mathcal{A}}}
\newcommand{\calc}{{\mathcal{C}}}
\newcommand{\calf}{{\mathcal{F}}}
\newcommand{\calfd}{{\calf_d}}
\newcommand{\calh}{{\mathcal{H}}}
\newcommand{\tcalh}{{\widetilde{\calh}}}
\newcommand{\calI}{{\mathcal{I}}}
\newcommand{\calhk}{\calh_d(K)}
\newcommand{\calg}{{\mathcal{G}}}
\newcommand{\calgd}{{\calg_d}}
\newcommand{\calM}{{\mathcal{M}}}
\newcommand{\caln}{{\mathcal{N}}}
\newcommand{\calp}{{\mathcal{P}}}
\newcommand{\cals}{{\mathcal{S}}}
\newcommand{\calu}{{\mathcal{U}}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\fA}{\mathfrak{A}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\fF}{\mathfrak{F}}
\newcommand{\fL}{\mathfrak{L}}
\newcommand{\fU}{\mathfrak{U}}
\newcommand{\fK}{{\mathfrak{K}}}
\newcommand{\hS}{\widehat{S}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
\newcommand{\bigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\bignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
\newcommand{\Bignorm}[2][{}]{\ensuremath{\Bigl \lVert #2 \Bigr \rVert}_{#1}}
\newcommand{\calm}{{\mathfrak{M}}}

\newcommand{\des}{\{\bx_i\}}
\newcommand{\desinf}{\{\bx_i\}_{i=1}^{\infty}}
\newcommand{\desn}{\{\bx_i\}_{i=1}^n}
\newcommand{\wts}{\{g_i\}_{i=1}^N}
\newcommand{\wtsn}{\{g_i\}_{i=1}^N}
\newcommand{\datan}{\{y_i\}_{i=1}^N}

%FJH added
\newcommand{\Order}{\mathcal{O}}
\newcommand{\ch}{\mathcal{H}}
\newcommand{\tch}{{\widetilde{\ch}}}
\newcommand{\veps}{\boldsymbol{\varepsilon}}
\DeclareMathOperator{\best}{best}
\newcommand{\hmu}{\hat{\mu}}
\newcommand{\hsigma}{\hat{\sigma}}
\newcommand{\tK}{\widetilde{K}}
%\newcommand{\MATLAB}{{\sc \MATLAB}\xspace}
\newcommand{\abstol}{\varepsilon_{\text{a}}}
\newcommand{\reltol}{\varepsilon_{\text{r}}}

\newcommand\starred[1]{\accentset{\star}{#1}}

\newcommand{\designInf}{\{\bx_i\}_{i=1}^\infty}
\newcommand{\dataN}{\bigl\{\bigl(\bx_i,f(\bx_i)\bigr)\bigr\}_{i=1}^n}
\newcommand{\dataNp}{\bigl\{\bigl(\bx_i,f(\bx_i)\bigr)\bigr\}_{i=1}^{n'}}
\newcommand{\dataNo}{\bigl\{\bigl(\bx_i,f(\bx_i)\bigr)\bigr\}_{i=1}^{n_0}}
\newcommand{\ErrN}{\ERR\bigl(\dataN,n\bigr)}
\newcommand{\fint}{f_{\text{int}}}
\newcommand{\inflate}{\fC}
\newcommand{\IIDSim}{\overset{\text{IID}}{\sim}}
\newcommand{\LDSim}{\overset{\text{LD}}{\sim}}


\definecolor{MATLABOrange}{rgb}{0.85,  0.325, 0.098}


%\setcounter{page}{1}


\setlist[description]{font=\normalfont\itshape, labelindent = 0.4cm}
\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\textit{#1.}}
\setlist[itemize]{leftmargin=3ex}
\setlist[enumerate]{leftmargin=5ex}

\makeatletter
\newenvironment{varsubequations}[1]
 {%
  \addtocounter{equation}{-1}%
  \begin{subequations}
  \renewcommand{\theparentequation}{#1}%
  \def\@currentlabel{#1}%
 }
 {%
  \end{subequations}\ignorespacesafterend
 }
\makeatother


\newcommand{\FJHNote}[1]{{\color{blue}Fred: #1}}
\newcommand{\AGSNote}[1]{{\color{cyan}Aleksei: #1}}
\newcommand{\SMNote}[1]{{\color{blue}Simon: #1}}
\newcommand{\SCTCNote}[1]{{\color{green}Sou-Cheng: #1}}
\newcommand{\YDNote}[1]{{\color{magenta}Yuhan: #1}}

% Notes on the paper for communicating with coauthors
\newif\ifnotesw \noteswtrue
\newcommand{\notes}[1]{\ifnotesw \textcolor{red}{  $\clubsuit$\ {\sf \bf \it  #1}\ $\clubsuit$  }\fi}
%\noteswfalse   % comment this line out to turn on style notes




\iffalse
All NSF proposals are evaluated through use of two National Science Board approved merit review criteria. In some instances, however, NSF will employ additional criteria as required to highlight the specific objectives of certain programs and activities.

The two merit review criteria are listed below. Both criteria are to be given full consideration during the review and decision-making processes; each criterion is necessary but neither, by itself, is sufficient. Therefore, proposers must fully address both criteria. (Chapter II.C.2.d(i) contains additional information for use by proposers in development of the Project Description section of the proposal.) Reviewers are strongly encouraged to review the criteria, including Chapter II.C.2.d(i), prior to the review of a proposal.

When evaluating NSF proposals, reviewers will be asked to consider what the proposers want to do, why they want to do it, how they plan to do it, how they will know if they succeed, and what benefits could accrue if the project is successful. These issues apply both to the technical aspects of the proposal and the way in which the project may make broader contributions. To that end, reviewers will be asked to evaluate all proposals against two criteria:
• Intellectual Merit: The Intellectual Merit criterion encompasses the potential to advance knowledge; and
• Broader Impacts: The Broader Impacts criterion encompasses the potential to benefit society and contribute to the achievement of specific, desired societal outcomes.

The following elements should be considered in the review for both criteria:
1. What is the potential for the proposed activity to:
	a. Advance knowledge and understanding within its own field or across different fields (Intellectual Merit); and
	b. Benefit society or advance desired societal outcomes (Broader Impacts)?
2. To what extent do the proposed activities suggest and explore creative, original, or potentially transformative concepts?
3. Is the plan for carrying out the proposed activities well-reasoned, well-organized, and based on a sound rationale? Does the plan incorporate a mechanism to assess success?
4. How well qualified is the individual, team, or organization to conduct the proposed activities?
5. Are there adequate resources available to the PI (either at the home organization or through
collaborations) to carry out the proposed activities?

Chapter II.C.2.d(i)
The Project Description should provide a clear statement of the work to be undertaken and must include the objectives for the period of the proposed work and expected significance; the relationship of this work to the present state of knowledge in the field, as well as to work in progress by the PI under other support.

The Project Description should outline the general plan of work, including the broad design of activities to be undertaken, and, where appropriate, provide a clear description of experimental methods and procedures. Proposers should address what they want to do, why they want to do it, how they plan to do it, how they will know if they succeed, and what benefits could accrue if the project is successful. The project activities may be based on previously established and/or innovative methods and approaches, but in either case must be well justified. These issues apply to both the technical aspects of the proposal and the way in which the project may make broader contributions.

The Project Description also must contain, as a separate section within the narrative, a section labeled “Broader Impacts”. This section should provide a discussion of the broader impacts of the proposed activities. Broader impacts may be accomplished through the research itself, through the activities that are directly related to specific research projects, or through activities that are supported by, but are complementary to the project. NSF values the advancement of scientific knowledge and activities that contribute to the achievement of societally relevant outcomes. Such outcomes include, but are not limited to: full participation of women, persons with disabilities, and underrepresented minorities in science, technology, engineering, and mathematics (STEM); improved STEM education and educator development at any level; increased public scientific literacy and public engagement with science and technology; improved well-being of individuals in society; development of a diverse, globally competitive STEM workforce; increased partnerships between academia, industry, and others; improved national security; increased economic competitiveness of the U.S.; use of science and technology to inform public policy; and enhanced infrastructure for research and education. These examples of societally relevant outcomes should not be considered either comprehensive or prescriptive. Proposers may include appropriate outcomes not covered by these examples.

Plans for data management and sharing of the products of research, including preservation, documentation, and sharing of data, samples, physical collections, curriculum materials and other related research and education products should be described in the Special Information and Supplementary Documentation section of the proposal (see Chapter II.C.2.j for additional instructions for preparation of this section).

For proposals that include funding to an International Branch Campus of a U.S. IHE or to a foreign organization (including through use of a subaward or consultant arrangement), the proposer must provide the requisite explanation/justification in the project description. See Chapter I.E for additional information on the content requirements.

Ideas:

Theory for higher-order nets
Error bounds with less emphasis on the design, e.g.,


\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\leftmargini}{2.5ex}
%% Shrink space before and after display environments
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}


\begin{center}
\textbf{\Large
	Budget Impact/Change of Scope Statement for \\
	\large
Cost-Efficient and Confident Sampling for \\ Modern Scientific Discovery
%Cost-Efficient Simulation of Scalable Scientific and Big Data Computation for Problems Involving Uncertainty.
%Project Description
}
\end{center}
%\vspace{-2ex}
%
%\setcounter{tocdepth}{1}
%\tableofcontents
%
%\vspace{-6ex}
% \FJHNote{Our title tells them what.  We need a short version of how.  How about something like

% \bigskip

% We will develop and extend highly stratified sampling methods and sound, data-based stopping criteria to solve new applications.}

We highlight under each proposed task what can and cannot be done in light of the budget reduction.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Developing Cost-Efficient and Confident Sampling}
\label{sec:tasks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bayesian Sampling for Expensive Posteriors} \label{sec:bayes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We will develop the proposed ESP sampler (with supporting methods and algorithms) as initially proposed. We will explore associated theoretical rates and central limit theorems if there are sufficient resources at the end of the project. These methods will be applied to physical science and engineering applications, as initially intended.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adaptive Multifidelity Algorithms} \label{sec:performance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

While we will extend our rigorous data-based stopping rules to multifidelity problems, the class of problems that we may be able to address during the life of the award will be somewhat \emph{smaller than} originally proposed.  New algorithms will be implemented and tested on real applications as originally proposed.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Big Data Subsampling} \label{sec:bigdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The development of the LD subsampling method will proceed as proposed. We will explore its implementation in a broad range of test cases, but its application for real-time UAV flight may be deferred unless there is sufficient time and resources at the end of the project.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Distribution, Density and Quantile Estimation} \label{sec:distdensquant}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The exploration of the effectiveness of LD Sequences for these important problems that are beyond computing integrals or expectations will proceed, but not as large in scope as originally proposed.  We will test our new methods on some industrial strength applications as originally proposed.




\section{Broader Impacts}

% \cmtS{``Broader Impacts and Implementation''? We can then discuss \QMCPy as an open-source vessel for disseminating the proposed framework, geared towards the goal of scientific progress \& engineering advancement, etc.}

\subsection{Dissemination to the Broad Scientific Community.}
Given the reduction in travel budget and the elimination of the budget to host visitors and pay for article processing charges, as recommended by the program director, our dissemination efforts may not be as effective as originally envisioned, however, we will use electronic communication to accomplish what we can with limited travel.



\subsection{QMCPy as a Proving Ground.} \label{sec:provingground}
We will continue to build our user and developer base of QMCPy as proposed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Promoting Proper QMC Practice and Code.} \label{sec:goodpractice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We will use online discussion groups along with some travel to grow the QMC community developing good code.



% Educating and Mentoring Cross-Disciplinary Computational Researchers
\subsection{Training the Next Generation of {\em Science-Based} Computational Researchers.}

Given the reduction in student support, we will look for other opportunities not funded by this grant to leverage what this grant provides to train computational researchers.  We have retained support for a PhD student for three years.

\subsection{Incorporating Diversity, Equity and Inclusion} We will look for collaborations with under-served groups outside what can now be funded by this grant, but we may not be able to fund as many summer students as originally planned.  We may request an REU supplement.

% % \subsection*{}
% \subsection{Expanding the Scope of QMC Applications} \label{sec:scopeapplication}



\end{document}

%%%%%%%%%%QMCPy%%%%%%%%%%%%%%%

.